|

### 2021-08-15 paper/dcpo_demsupport.Rmd
include dotwhisker::small_multiple() hacks

# Theme setup
theme_set(theme_minimal())
```

>>>>

# dotwhisker::small_multiple() hacks
body(small_multiple)[[17]] <- substitute(
    p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
                        x = as.factor(model), colour = submodel)) +
        do.call(geom_pointrange, point_args) + ylab("") + xlab("") + 
        facet_grid(term ~ .,
                   scales = "free_y",
                   labeller = label_parsed,    # enable LaTeX facet labels
                   switch = "y") +             # put facet labels on left
        scale_y_continuous(position = "right") # put axis label on right
)
```
